STA107 Post-Course Survey Analysis

### 2025-04-14 paper/paper.qmd
added quantitative analysis

---
title: "STA107 Post-Course Survey Analysis"
subtitle: "Evaluating Student Reflections on R and Statistical Learning"
author: 
  - Sinan Ma
  - Jaiditya Dev
date: "April 13, 2025"
format: 
  pdf:
    toc: true
    number-sections: true
    code-fold: true
    code-summary: "Show Code"
    fig-align: center
    fig-cap-location: top
    keep-tex: true
---

@@

#### import survey data ####
data <- read_csv("../data/clean_data.csv")
qualitative_data <- read_csv("../data/qualitative_analysis_data.csv")
# change to clean data later
```

@@

### Qualitative Analysis
```{r}
# Load required libraries
library(tidyverse)
library(stringr)
library(tidytext)
library(syuzhet)
library(ggplot2)
library(tidyr)
library(wordcloud)

@@

for (qn in question_names) {
  analyze_sentiment(qn, qn)
}
```

# Results

@@

- Distribution of responses to Likert-scale questions
- Summary statistics (mean, median, SD)
- Visualizations: bar plots, histograms

>>>>

---
title: "STA107 Post-Course Survey Analysis"
subtitle: "Evaluating Student Reflections on R and Statistical Learning"
author: 
  - Sinan Ma
  - Jaiditya Dev
date: "April 13, 2025"
format: 
  pdf:
    toc: true
    number-sections: true
    code-fold: true
    code-summary: "Show Code"
    fig-align: center
    fig-cap-location: top
    keep-tex: true
execute:
  echo: false  
  warning: false
  message: false
---

@@

#### import survey data ####
data <- read_csv("../data/clean_data.csv")
qualitative_data <- read_csv("../data/qualitative_analysis_data.csv")
quantitative_data <- read_csv("../data/quantitative_analysis_data.csv")
```

@@

## Quantitative Analysis
```{r}
# Clean column names
colnames(quantitative_data) <- colnames(quantitative_data) %>%
  tolower() %>%
  str_replace_all(" ", "_") %>%
  str_replace_all("^x", "")

# Select and rename Likert-scale columns
quantitative_data <- quantitative_data[, 1:6]
colnames(quantitative_data) <- c(
  "Stat_Communication_Before_Course",
  "Stat_Communication_After_Course",
  "R_Skills_Before_Course",
  "R_Skills_After_Course",
  "Understanding_After_Assignments",
  "Understanding_After_Tutorials"
)
```

### Communication Ability Before vs. After
```{r}
comm_data <- quantitative_data %>%
  select(Stat_Communication_Before_Course, Stat_Communication_After_Course) %>%
  pivot_longer(cols = everything(), names_to = "Question", values_to = "Rating") %>%
  drop_na()

ggplot(comm_data, aes(x = factor(Rating), fill = Question)) +
  geom_bar(position = "dodge") +
  theme_minimal() +
  labs(title = "Ability to Communicate Statistics: Before vs. After",
       x = "Rating (1 = Lowest, 5 = Highest)", y = "Count") +
  scale_fill_manual(values = c("Stat_Communication_Before_Course" = "#66c2a5", "Stat_Communication_After_Course" = "#fc8d62"))
```

The histogram shows a clear improvement in students' perceived communication ability. More students rated themselves at level 4 or 5 after the course compared to before, indicating that the course helped them gain confidence in articulating statistical ideas.

### R Ability Before vs. After
```{r}
r_data <- quantitative_data %>%
  select(R_Skills_Before_Course, R_Skills_After_Course) %>%
  pivot_longer(cols = everything(), names_to = "Question", values_to = "Rating") %>%
  drop_na()

ggplot(r_data, aes(x = factor(Rating), fill = Question)) +
  geom_bar(position = "dodge") +
  theme_minimal() +
  labs(title = "Ability to Use R: Before vs. After",
       x = "Rating (1 = Lowest, 5 = Highest)", y = "Count") +
  scale_fill_manual(values = c("R_Skills_Before_Course" = "#8da0cb", "R_Skills_After_Course" = "#e78ac3"))
```

Students entered the course with relatively low self-reported R skills (mostly 1s and 2s), but after completing the course, a majority rated themselves at 3 or higher. This shift demonstrates the course’s success in introducing R programming effectively.

### Understanding After Assignments vs. Tutorials
```{r}
concept_data <- quantitative_data %>%
  select(Understanding_After_Assignments, Understanding_After_Tutorials) %>%
  pivot_longer(cols = everything(), names_to = "Question", values_to = "Rating") %>%
  drop_na()

ggplot(concept_data, aes(x = factor(Rating), fill = Question)) +
  geom_bar(position = "dodge") +
  theme_minimal() +
  labs(title = "Understanding of Statistical Concepts: Assignment vs. Tutorial",
       x = "Rating (1 = Lowest, 5 = Highest)", y = "Count") +
  scale_fill_manual(values = c("Understanding_After_Assignments" = "#a6d854", "Understanding_After_Tutorials" = "#ffd92f"))
```

Students found both tutorials and assignments useful for understanding statistical concepts, with a slight preference for tutorials. The higher number of level 4 and 5 responses for tutorials suggests that real-time, interactive support may have been especially beneficial.

## Qualitative Analysis
```{r}
# Load required libraries
library(tidyverse)
library(stringr)
library(tidytext)
library(syuzhet)
library(ggplot2)
library(tidyr)
library(wordcloud)

@@

for (qn in question_names) {
  analyze_sentiment(qn, qn)
}
```
# Results

@@

The survey included six Likert-scale questions aimed at capturing students’ self-perceived development in statistical understanding and communication, both before and after the course. The questions also addressed students’ ability to use R software and their comprehension of statistical concepts through tutorials and weekly assignments.

Key findings include:

- **Improved Communication Skills**: Students reported a notable improvement in their ability to communicate statistics, with the average post-course rating (M = 3.92) higher than the pre-course rating (M = 3.09).
- **Increased R Proficiency**: The mean rating for R software usage rose from 2.43 before the course to 3.49 after completing it, indicating significant growth in computational skills.
- **Conceptual Understanding**: Understanding of statistical concepts improved through both tutorials (M = 4.09) and weekly assignments (M = 3.84), with tutorials being rated slightly more helpful on average.

The graphs above illustrate the distribution of responses across the three themes: communication, R proficiency, and statistical understanding.
